Gait Monitoring using Wireless Sensors\\ \vspace{4mm} \large{Final Report 18-748}\\ \large{Spring 2017}

### 2017-05-10 paper.tex
Added user interface description and utodo's

@@

\usepackage{balance}
\usepackage{comment}
\usepackage{xspace}
\usepackage[export]{adjustbox}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage{float}
\usepackage{subfigure}
\newcommand{\sys}{Safewalk\xspace}
\author{
  \IEEEauthorblockN{
   Iljoo Baek, Mengwen He and Emily Ruppel
  }
 \IEEEauthorblockA{
   Carnegie Mellon University
  }
 \IEEEauthorblockA{
   {ibaek,mengwenhe,eruppel}@andrew.cmu.edu
  }
}
\title{Gait Monitoring using Wireless Sensors\\
        \vspace{4mm}
        \large{Final Report 18-748}\\
        \large{Spring 2017}}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.75\columnwidth]{figs/cropped2}
  \caption{{\bf Firefly node with IMU board attached}}
  \label{fig:ff}
\end{figure}

@@

\subsection{Gait Analysis}
Our work analyzing subject's gait parameters focused on stride length, swing time, and
knee extension. Each of these parameters required different analysis techniques that will
be described below.\\ 
{\bf Stride Length} To determine the stride length, we first assume that the lengths of each
segment of a subject's limbs are known. Then...\\
%Need to know how this works!!
{\bf Swing Time} Our analysis focuses on detecting the subject's step to in turn ascertain
when a subject's foot is on the ground, and when it is in motion. By making the assumption
that the acceleration of the foot is close to zero when it is on the ground, we were able
to detect the beginning and end of a subject's stride based strictly on acceleration data
from the x-y plane. Our implementation is a simplified version of the technique used
in~\cite{fancy}. Figure~\ref{fig:step-detect} shows the basic shape of accelerometer data
gathered from a subject's feet as he or she walks and the marked regions indicate the time
during which his/her foot is either on the ground or in the air. 
\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/swing}
  \caption{{\bf Step detection from accelerometer data}}
  \label{fig:step-detect}
\end{figure}
\\
{\bf Knee Extension} A subject's knee extension was calculated using the hinge joint
techniques explained by Yost~\cite{yost}. The equations are: 
%Insert equations here!!

@@

\subsection{User Interface}

@@

\section{Results}

Talk about all of the calculations and provide examples from data we have lying around.

>>>>

\newcount\draft\draft=1 % set to 0 for submission or publication
\newcount\cameraready\cameraready=1

@@

\usepackage{balance}
\usepackage{comment}
\usepackage{xspace}
\usepackage{xxx}
\usepackage[export]{adjustbox}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage{float}
\usepackage{subfigure}
\newcommand{\sys}{Safewalk\xspace}
\newcommand{\utodo}[2]{ {\textcolor{red} {#1}}: {\textcolor{red} {#2}}}
\author{
  \IEEEauthorblockN{
   Iljoo Baek, Mengwen He and Emily Ruppel
  }
 \IEEEauthorblockA{
   Carnegie Mellon University
  }
 \IEEEauthorblockA{
   {ibaek,mengwenhe,eruppel}@andrew.cmu.edu
  }
}
\title{Gait Monitoring using Wireless Sensors\\
        \vspace{4mm}
        \large{Final Report 18-748}\\
        \large{Spring 2017}}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.6\columnwidth]{figs/cropped2}
  \caption{{\bf Firefly node with IMU board attached}}
  \label{fig:ff}
\end{figure}

@@

\subsection{Gait Analysis}
Our work analyzing subject's gait parameters focused on stride length, swing time, and
knee extension. Each of these parameters required different analysis techniques that will
be described below.\\ 
{\bf Stride Length} To determine the stride length, we first assume that the lengths of each
segment of a subject's limbs are known. \utodo{Alex}{Describe how stride length was
calculated}
\\
{\bf Swing Time} Our analysis focuses on detecting the subject's step to in turn ascertain
when a subject's foot is on the ground, and when it is in motion. By making the assumption
that the acceleration of the foot is close to zero when it is on the ground, we were able
to detect the beginning and end of a subject's stride based strictly on acceleration data
from the x-y plane. Our implementation is a simplified version of the technique used
in~\cite{fancy}. Figure~\ref{fig:step-detect} shows the basic shape of accelerometer data
gathered from a subject's feet as he or she walks and the marked regions indicate the time
during which his/her foot is either on the ground or in the air. \\
\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/swing}
  \caption{{\bf Step detection from accelerometer data}}
  \label{fig:step-detect}
\end{figure}
{\bf Knee Extension} A subject's knee extension was calculated using the hinge joint
techniques explained by Yost~\cite{yost}. The equations are \utodo{Iljoo}{Add the
equations you actually used for knee extension} Figure~\ref{fig:knees} shows the angles
that are reported by the final calculation.

@@

\subsection{User Interface}
\utodo{Alex}{Add all the details about the user interface that I missed!!}
The user interface is aimed at a technical professional rather than a healthcare provider,
but it is built so that certain features are easy to access for non-technical personnel
and data storage for future processing is streamlined. Our design uses the popular Robot
Operating System (ROS) platform to control data flow into the system software from the
single stream of data coming from the master node. The control buttons for data from the
individual nodes are simple to access and can be used to change the system's
configuration. The interface also contains a slave node health status indicator that
reports whether or not the master node has successfully received data from a given slave
within a recent timeframe. Figure~\ref{fig:ROS} shows the configuration interface and the
health status indicator. In a healthcare environment, these tools would be used by
technical personnell to configure the system software before it is used by a healthcare
provider.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/gui}
  \caption{{\bf ROS user interface}}
  \label{fig:gui}
\end{figure}
The user interface also provides a convenient video playback feature than can replay all
of the data visualizations produced in real time during active data capture as well as an
accompanying video of the subject. Finally, the data are logged automatically for future
use or offline analyses.

@@

\section{Results}
\
